\documentclass{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage[margin=0.5in]{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   		% ... or a4paper or a5paper or ...

\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps with pdflatex; use eps in DVI mode
\usepackage{enumerate}								% TeX will automatically convert eps --> pdf in pdflatex		


\title{Individual Performance Review\\ IN719 Systems Administration}
\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

\section*{Introduction}
The purpose of this assessment is to evaluate your working practices.  We want to see that you are working like a sysadmin should.  The assessment has three parts:

\begin{enumerate}
  \item  \textbf{Self assessment:}  You will evaluate your own performance and provide evidence to support your claims;
  \item  \textbf{Peer assessment:}  You will evaluate your team partner using the same measures that you used for your self assessment;
  \item  \textbf{Lecturer assessment:}  The lecturers will evaluate and comment on your performance.
\end{enumerate}

Note that on the self and peer assessments, your marks are based on how complete, accurate, and well-supported your assessments are. So if you claim that you are completing tickets promptly, then state what your mean time to resolve tickets is. If you claim you're keeping documentation up-to-date, then show your wiki edit history, and so on.

Also, when evaluating your work, keep in mind that it's not expected that you have been doing everything perfectly all the time. What is expected is that you have been improving over the past several weeks.

\section*{Marking schedule}
\textbf{Self assessment (20 marks):}

\begin{itemize}
  \item 20 - Insightful and accurate assessment of performance supported by ample clear evidence.
  \item 15 - Accurate assessment of performance well supported by evidence.
  \item 12 - Mainly accurate assessment of performance with some gaps in evidence.
  \item 8 - Mainly accurate assessment, but with little or no evidence provided.
  \item 5 - Assessment of performance not accurate and/or lacking in evidence .
\end{itemize}

\textbf{Peer assessment (10 marks):}

\begin{itemize}
  \item 10 - Accurate assessment of performance well supported by evidence.
  \item 7 - Mainly accurate assessment of performance with some gaps in evidence.
  \item 3 - Mainly accurate assessment, but with little or no evidence provided.
  \item 1 - Assessment of performance not entirely accurate and/or lacking in evidence .
\end{itemize}

\vskip 5mm

\textbf{Lecturer assessment:} The lecturer's assessment is broken down into the following areas.

\textbf{Ticketing (25 marks):}
\begin{itemize}
  \item 25 - All nontrivial tasks are tracked in ticket system. Tickets are strongly documented or linked to documents.  All tickets are promptly resolved.
  \item 20 - Significant tasks are tracked with tickets which are promptly handled.  Useful comments or other documents are included in most tickets.
  \item 15 - Tasks are typically tracked by tickets, but some gaps are noted.  Minimal but sufficient documentation is included.  Most tickets handled promptly.
  \item 10 - Few tickets are found that were not submitted by the lecturer.  Documentation often lacking.  A significant number of tickets not handled promptly.
  \item 5 - No tickets are found that were not submitted by the lecturer.  Documentation generally insufficient.  Tickets are not generally handled promptly.
\end{itemize}


\textbf{Documentation (25 marks):}
\begin{itemize}
  \item 25 - Extremely comprehensive and accurate documentation of all hosts, software, and procedures.  Wiki history shows frequent updating throughout the term.
  \item 20 - Quality documentation of hosts, software and procedures.  Only trivial gaps or errors noted.   Regular updates in recent weeks.
  \item 15 - Good documentation, but some noteworthy gaps or errors are found.  Adequate detail or clarity missing in some cases.
  \item 10 - Minimal documentation, often of poor quality.
  \item 5 -  Poor quality documentation with inadequate coverage.
\end{itemize}

\textbf{Time management (10 marks):}

Note that we use the term ``diary'' to refer to any structured time management tool suitable for our purposes.
\begin{itemize}
  \item 10 - Student presents a diary that shows excellent planning of all Polytech tasks on a consistent basis.
  \item 7 - Student presents a diary that shows reasonable planning of tasks in this paper but omits other Polytech work.
  \item 5- Student presents a diary that shows planning of many tasks in this paper, but with some notable gaps.
  \item 2 -  Student presents a diary that shows little planning of tasks.
\end{itemize}

\textbf{Teamwork (10 marks):}
\begin{itemize}
  \item 10 - Student is doing at least a fair share of the work and all teammates are very well informed about each others' work.  Excellent use of teamwork is evidenced by ticketing, source code repository activity, wiki edits, etc.  The team has a schedule that provided good distribution of coverage.
  \item 7 -  Student does a fair share of work and all teammates are generally informed, but some small gaps may be noted.
  \item 5 -  Student is doing a fair or nearly fair share of work, but teammates may be poorly informed about each others work.
  \item 2 -  Students is not doing a fair share of work and team communication appears to be poor.
\end{itemize}

\vskip 5mm

You will submit hard copies of your individual and peer assessment forms by noon on Friday, 17 April, You will have an in-person appointment with a lecturer after the term break to receive the lecturer feedback portion of the assessment. Given the COVID-19 situation we will see how these meetings will be handled later. You can use the form below for your assessment or create a similar document with a word processor or whatever it is you young people use these days.


\newpage

\section*{Self assessment}

Your name: 
\vskip 1cm

\subsection*{Ticketing}

Key indicators: 

1.  Are you responding to tickets and closing them promptly?

2.  Are you adding useful comments to tickets?

3.  Are you linking tickets to relevant wiki pages and/or linking to tickets from your wiki?

4.  Are you opening tickets to track tasks that are performed?

5.  Are you using tickets to communicate with your team and divide responsibilities for tasks?

Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\vskip 5cm



\subsection*{Documentation}

Key indicators: 

1.  Are your team documents kept accurate and complete ?

2.  Are you contributing to the wiki?

3.  Do you consult your wiki when working on tasks?

Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\newpage

\subsection*{Time management}

Key indicators: 

1.  Do you use a diary?

2.  Do you plan your work each morning and enter it into your diary?

3.  Do you review your diary at the end of each day and carry over unfinished tasks?

4.  Do you have a schedule with your team that allows you time for other papers and free time?

5.  Are you keeping up with your other papers?

Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\vskip 5cm

\subsection*{Teamwork}

Key indicators: 

1.  Are you sharing the work fairly with your team?

2.  Are you communicating with your team?


Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\vskip 4cm
    
\newpage

\section*{Peer assessment}

Name of teammate you are assessing: 
\vskip 1cm

\subsection*{Ticketing}

Key indicators: 

1.  Does this person repond to tickets and closing them promptly?

2.  Does this person add useful comments to tickets?

3.  Does this person link tickets to relevant wiki pages and/or linking to tickets from your wiki?

4.  Does this person open tickets to track tasks that are performed?

5.  Does this person use tickets to communicate with your team and divide responsibilities for tasks?

Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\vskip 5cm



\subsection*{Documentation}

Key indicators: 

1.  Is this person contributing to the wiki?

2.  Does this person consult the wiki when working on tasks?

Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\newpage

\subsection*{Time management}

Key indicators: 

1.  Does this person  use a diary?

2.  Is this person able to complete tasks in a reliable and timely manner ?

3.  Is this person keeping up with other papers?

Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\vskip 5cm

\subsection*{Teamwork}

Key indicators: 

1.  Is this person sharing the work fairly with your team?

2.  Is this person communicating with your team?


Overall rating: \hskip 1cm 1 \hskip 1cm 2 \hskip 1cm 3 \hskip 1cm 4 \hskip 1cm 5 

Comments:

\vskip 4cm
\end{document}
