% Beamer slide template prepared by Tom Clark <tom.clark@op.ac.nz>
% Otago Polytechnic
% Dec 2012

\documentclass[10pt]{beamer}
\usetheme{CambridgeUS}
\usepackage{graphicx}
\usepackage{fancyvrb}


\title{Accounting}

\author[IN618]{Introduction to IT Security}
\institute[Otago Polytechnic]{
  Otago Polytechnic \\
  Dunedin, New Zealand \\
}
\date{}
\begin{document}

%----------- titlepage ----------------------------------------------%
\begin{frame}[plain]
  \titlepage
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Review}

 AAA

 \begin{itemize}
	 \item Authentication: who you are 
	 \item Authorisation: what you can do
	 \item \textbf{Accounting: tracking what you have done}
 \end{itemize}
\end{frame}

%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Two parts to accounting}

 \begin{enumerate}
  \item Logging events
  \item Reviewing logs
  \end{enumerate}
\end{frame}

%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Logging events}

  Any application of any importance should write logs.
 \begin{itemize}
  \item Log any problems or exceptions that could indicate a bug.
  \item Log events that could represent a security issue like a failed login.
  \item You may want to log apparent user errors.
  \item You may want to log routine events if your application has security-sensitive function.
  \item Be wary of over-logging.  You will train users to ignore your logs if they contain useless information.
  \end{itemize}
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{How to log}

 \begin{itemize}
  \item Usually we write to a log file.
	  \begin{itemize} 
		  \item This is simple to do.
		  \item Operating systems already include this capability.  (e.g., Windows event viewer, Unix/Linux syslog)
		  \item It's easy to set up other programs to monitor and process logs.
	  \end{itemize}
  \item Occasionally, an application may log events in a database in order to support more complex built in event reporting.

  \end{itemize}
\end{frame}



%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Remote logging}

  For large or security-intensive applications, consider logging to a remote server.
 \begin{itemize}
  \item Logs are preserved even if the system running the application is compromised.
  \item It's easier to check and manage centralised logs.
  \end{itemize}
\end{frame}



%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Log levels}

 \begin{itemize}
  \item Logging services usually support a number of logging levels, e.g. informational, warning, error.
  \item Application configuration should include selection of log level.
  \item This helps avoid over-logging.
  \end{itemize}
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Monitoring  logs}

 \begin{itemize}
  \item We can, and do, view logs manually.
  \item If we have a large volume of logs, we may use software to process and summarise the logged data.
  \item We may use monitoring programs to checked logs in near real time to alert us to problems.
  \item Seperating responsibility for writing logs from the responsibility for monitoring logs
	  \begin{itemize}
		  \item means that application programmers don't have to anticipate user security demands;
		  \item gives users the flexibility to design and implement their own log monitoring protocol.
          \end{itemize}
  \end{itemize}
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Log handling and retention}

 Now that we are producing and reviewing lots of logs, we need a plan for retention.
 \begin{itemize}
  \item This is a policy decision balancing security needs with storage and handling capacity.
  \item In some areas there may be legal or regulatory concerns.
  \item Consider storing logs on secured write-only media.
  \end{itemize}
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Today's lab}

  We will take the password checking program we wrote last week and add logging to it.
\end{frame}

\end{document}

