% Beamer slide template prepared by Tom Clark <tom.clark@op.ac.nz>
% Otago Polytechnic
% Dec 2012

\documentclass[10pt]{beamer}
\usetheme{Dunedin}
\usepackage{graphicx}
\usepackage{fancyvrb}

\newcommand\codeHighlight[1]{\textcolor[rgb]{1,0,0}{\textbf{#1}}}

\title{Documentation}

\author[IN719]{Systems Administration}
\institute[Otago Polytechnic]{
  Otago Polytechnic \\
  Dunedin, New Zealand \\
}
\date{}
\begin{document}

%----------- titlepage ----------------------------------------------%
\begin{frame}[plain]
  \titlepage
\end{frame}

%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{}
   
   
   In the first session we observed that a key responsibility of sysadmins 
   is to know the states of their systems. Since most of us do not have perfect
   memories, nor can we read minds, it's important to document this.
\end{frame}

%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Document repositories}
   
   We need some tools to access our documentation. We will use a wkik.
   
   \begin{itemize}
     \item It is accessible over the Internet from anywhere from which we will work.
     \item It is accessible on a wide range of devices.
     \item It doesn't have a lot of dependencies.
     \item It automatically tracks metadata.
   \end{itemize}
  
  
\end{frame}

%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{What goes on our wiki}
   
   \begin{itemize}
     \item Step-by-step procedures for tasks that are, or may be done repeatedly.
     \item A list of all the machines with information about each one.
     \item A page with team members, contact information, and an on-call schedule.
     \item For each service we deploy, a section in the Ops Doc format:
       \begin{enumerate}
         \item Overview
         \item Build (We can omit this one.)
         \item Deploy
         \item Common Tasks
         \item Pager Playbook
         \item Disaster Recovery Plan
         \item Service Level Agreement (SLA)
         \end{enumerate}
   \end{itemize}
  
  We won't have a lot of information to put in these to begin, but get the framework in place
  and add the specific information over time.
  
  
\end{frame}

%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Security considerations}
   
   Our wiki is password protected, so we can put information that is not public, 
   but do not put any security sensitive information on it.
  
  
\end{frame}

\end{document}
