% Beamer slide template prepared by Tom Clark <tom.clark@op.ac.nz>
% Otago Polytechnic
% Dec 2012

\documentclass[10pt]{beamer}
\usetheme{CambridgeUS}
\usepackage{graphicx}
\usepackage{fancyvrb}


\title{Physical Security}

\author[IN618]{Introduction to IT Security}
\institute[Otago Polytechnic]{
  Otago Polytechnic \\
  Dunedin, New Zealand \\
}
\date{}
\begin{document}

%----------- titlepage ----------------------------------------------%
\begin{frame}[plain]
  \titlepage
\end{frame}



%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Physical Security}


  Physical security is

 \begin{itemize}
  \item the most overlooked part of IT security, and
  \item the source of some of the most easily exploitable vulnerabilities.
 \end{itemize}

 It is also a good example of how security is always a trade-off versus
 convenience.

\end{frame}



%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Servers/Core Hardware}


 \begin{itemize}
  \item Should be in locked equipment rooms
  \item Access should be monitored
  \item Equipment should be properly secured in racks
 \end{itemize}
\end{frame} 


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Network access}


 \begin{itemize}
  \item Unsecured open wired access points should be disconnected.
  \item Wireless access areas should be mapped out.  Avoid giving wireless
	  coverage in areas that are physically insecure.
 \end{itemize}
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Work stations}


 \begin{itemize}
  \item Should be in physically secure areas.
  \item May also need to be locked to their locations.
  \item Should have BIOS passwords (and correct boot device order).
  \item In some cases, a case lock should be used.
  \item In some (more extreme) cases, usb and other ports should be disabled.
  \item Consider hard drive encryption.
 \end{itemize}
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Printers}

Some printers/copiers/scanners store copies of recent files in memory and
need to be secured.

\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Removable media}


 \begin{itemize}
  \item Backup tapes
  \item USB keys
  \item Old printouts
 \end{itemize}
 
 May all have sensitive data on them and need to be handled properly
\end{frame}


%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Portable devices}


 \begin{itemize}
  \item Portable devices have all of the problems that workstations have, but
  \item We don't have some of the options of physically securing them.
  \item Things like hard drive encryption and remote control tools are even more important.
 \end{itemize}
\end{frame}
%----------- slide --------------------------------------------------%
\begin{frame}
  \frametitle{Device disposal}


 \begin{itemize}
  \item Anything that stores data should be wiped clean or otherwise disabled before
	  they are taken out of inventory.
 \end{itemize}
\end{frame}

\end{document}

